Pillar 1 - Sequential Pattern Mining

### 2019-02-14 Pillar 1 - Sequential Pattern Mining.Rmd
simplify code for summary statistics

  data %>%
    filter(
      !is.na(!!enquo(var))
      ) %>%
    group_by(
      !!enquo(var)
      ) %>%
    summarise(
      Min             = min(Grade),
      Max             = max(Grade), 
      Mean            = mean(Grade), 
      Median          = median(Grade), 
      SD              = sd(Grade),
      `Failure Rate`  = mean(Fail),
      `Failure Count` = sum(Fail),
      Count           = n()
      ) %>%
    mutate_at(
      vars(Mean, SD, `Failure Rate`),
      round,
      digits = 2
    )

@@

# Course level
statistics$course <- d_transcript %>%
  inner_join(
    d_course,
    by = c("Course ID")
    ) %>%
  provide_statistics(`Course ID`)

# Cluster level
statistics$cluster <- d_transcript %>%
  inner_join(
    d_course, 
    by = "Course ID"
    ) %>%
  provide_statistics(Cluster)

# Type level
statistics$type <- d_transcript %>%
  inner_join(
    d_course, by = "Course ID"
    ) %>%
  provide_statistics(Type)

# Concentration evel
statistics$concentration <- d_transcript %>%
  inner_join(
    d_course,
    by = "Course ID"
    ) %>%
  gather(
    key = X, 
    value = Concentration, 
    Concentration, `Concentration (additional)`,
    na.rm = TRUE
    ) %>%
  provide_statistics(Concentration)

@@

# Level level
statistics$level <- d_transcript %>%
  # TODO: filter for student who completed their studies
  inner_join(d_course, by = c("Course ID")) %>%
  provide_statistics(Level)

>>>>

  data %>%
    filter(
      !is.na(!!enquo(var))
      ) %>%
    group_by(
      !!enquo(var)
      ) %>%

    summarise(
      Count           = n(),
      Min             = min(Grade),
      Max             = max(Grade),
      Mean            = mean(Grade),
      Median          = median(Grade),
      IQR             = IQR(Grade),
      SD              = sd(Grade),
      `Low Rate`      = mean(Grade < high_grade),
      `Fail Rate`  = mean(Grade < pass_grade)
      ) %>%

    mutate_at(
      vars(Mean, SD, `Low Rate`, `Fail Rate`),
      round,
      digits = 2
    )

# for convenience
join_d_course <- function(data){

  data %>%
    inner_join(
    d_course,
    by = c("Course ID")
    )

@@

# Course level
statistics$course <- d_transcript %>%
  join_d_course %>%
  provide_statistics(`Course ID`)

# Cluster level
statistics$cluster <- d_transcript %>%
  join_d_course %>%
  provide_statistics(Cluster)

# Type level
statistics$type <- d_transcript %>%
  join_d_course %>%
  provide_statistics(Type)

# Concentration evel
statistics$concentration <- d_transcript %>%
  join_d_course %>%
  gather(
    key = X, 
    value = Concentration, 
    Concentration, `Concentration (additional)`,
    na.rm = TRUE
    ) %>%
  provide_statistics(Concentration)

@@

# Level level
statistics$level <- d_transcript %>%
  # TODO: filter for student who completed their studies
  join_d_course %>%
  provide_statistics(Level)
